The Astropy Project:

### 2017-09-20 main.tex
Update on Overleaf.

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{July 1, 2016}
%\revised{September 27, 2016}

%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.1 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%

@@

\title{Astropy - New software standards for a growing community}

%%
%% The \author command is the same as before except it now takes an optional
%% arguement which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid.
%%
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.1 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

\correspondingauthor{Astropy Coordinating committee or First Author}
\email{coordinators@astropy.org}

\author{Astropy Project}

@@

\section{Major concepts}
\subsection{Astropy development model, astropy ecosystem}
This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.
\subsection{Mixin}
\subsection{Accuracy testing across many different implementation}

@@

\subsection{Constants}
versioning

@@

\subsubsection{Key features}

- Celestial coordinates, and local coordinates (via EarthLocation + Time)
- JPL ephemerids

\subsection{Units and quantities}

@@

\subsection{Convolution}
Astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.

@@

\subsection{Modeling}
The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.

@@

\section{Tutorials, Snippets, Gallery}

\section{Outlook}
dropping python2 support, growths of affiliated packages
Summary

>>>>

\submitjournal{ApJ}

@@

\title{The Astropy Project: }

\correspondingauthor{Astropy coordination committee}
\email{coordinators@astropy.org}

\author{Astropy Collaboration}

@@

\section{Major concepts}
\subsection{Astropy development model, astropy ecosystem}
This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.
\subsection{Mixin}
\subsection{Accuracy testing across many different implementation}
\subsection{Use of Quantities across package}

@@

% \subsection{Analytic Functions}

\subsection{Constants}
% David S.
versioning

@@

\textbf{Key features}

\begin{itemize}
	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
	\item JPL ephemerids
\end{itemize}

\subsection{Units and quantities}
% Marten, Adrian

@@

\subsection{Convolution}
% Adam G.

Astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.

@@

\subsection{Modeling}
% Nadia

The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.

@@

\section{Learning Astropy}
% Kelle & Adrian?

Explain components: Documentation, Example gallery, Tutorials and lessons

\section{The future of the Astropy project}

dropping python2 support, growths of affiliated packages
Summary
